Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2016-07-08 inst/examples/20160715-slides-Krakow.Rmd
s

# TITLE COUNT
p1 <- ggplot(df, aes(x = period, y = n)) +
       geom_bar(stat = "identity", position = "stack") +
       scale_x_discrete(labels = c("Period A", "Period B")) +
       ggtitle("Title count")

# PAPER
p2 <- ggplot(df, aes(x = period, y = paper)) +
       geom_bar(stat = "identity", position = "stack") +
       scale_x_discrete(labels = c("Period A", "Period B")) +
       ggtitle("Paper")

>>>>

# TITLE COUNT
p1 <- ggplot(df, aes(x = period, y = n)) +
       geom_bar(stat = "identity", position = "stack") +
       scale_x_discrete(labels = c("1759-1765", "1766-1772")) +
       ggtitle("Title count") + xlab("1759-1765")

# PAPER
p2 <- ggplot(df, aes(x = period, y = paper)) +
       geom_bar(stat = "identity", position = "stack") +
       scale_x_discrete(labels = c("1759-1765", "1766-1772")) +
       ggtitle("Paper consumption") + xlab("1766-1772")
